Comparison of FDR methods on GWAS with SummarizedBenchmark

### 2017-10-26 datasets/GWAS/GWAS-SummarizedBenchmark.Rmd
Calculate Zscore from pvals instead of effect/SE

```{r, GWAS1-reformat}
bmi <- bmi %>% 
        dplyr::rename(pval = p_value,
               SE = stderr,
               effect_size = effect,
               ind_covariate = N) %>%
        mutate(test_statistic = effect_size/SE) %>%
        select(pval, SE, effect_size, ind_covariate, test_statistic)

>>>>

```{r, GWAS1-reformat}
bmi <- bmi %>% 
        dplyr::rename(pval = p_value,
               SE = stderr,
               effect_size = effect,
               ind_covariate = N) %>%
        mutate(test_statistic = qnorm(exp(log(pval)-log(2)), lower.tail=FALSE) * sign(effect_size)) %>%
        select(pval, SE, effect_size, ind_covariate, test_statistic)
